Political Polarization, Public Trust, and Healthcare Disparities: Unraveling COVID-19's Impact and Future Preparedness

### 2024-02-15 outputs/paper/paper.qmd
fixed ref

Various studies and our results have consistently demonstrated a correlation between political affiliation and adherence to health guidelines during the COVID-19 pandemic. This correlation extends to distinct behaviors and compliance levels with health recommendations, directly impacting COVID-19 case rates and mortality. One study, in particular, revealed a noteworthy trend: while Democratic-leaning states initially faced higher cases and death rates at the onset of the pandemic, Republican-leaning states ultimately suffered more severely throughout the latter half of 2020 [@march 11_2021_2021]. This shift in severity can be attributed to several factors. Initially, many Democratic states were the epicenter of the virus, experiencing high case and death rates due to the initial entry of the virus into these regions. However, as the pandemic progressed, Republican-leaning states saw a surge in cases, partially due to their relatively loose COVID-19 regulations, such as the lack of strict mask requirements [@march 11_2021_2021].

>>>>

Various studies and our results have consistently demonstrated a correlation between political affiliation and adherence to health guidelines during the COVID-19 pandemic. This correlation extends to distinct behaviors and compliance levels with health recommendations, directly impacting COVID-19 case rates and mortality. One study, in particular, revealed a noteworthy trend: while Democratic-leaning states initially faced higher cases and death rates at the onset of the pandemic, Republican-leaning states ultimately suffered more severely throughout the latter half of 2020 [@march_11_2021_2021]. This shift in severity can be attributed to several factors. Initially, many Democratic states were the epicenter of the virus, experiencing high case and death rates due to the initial entry of the virus into these regions. However, as the pandemic progressed, Republican-leaning states saw a surge in cases, partially due to their relatively loose COVID-19 regulations, such as the lack of strict mask requirements [@march_11_2021_2021].
